Stepwise Multiple Regressions

### 2021-02-23 Stepwise Multiple Regressions.Rmd

---
title: "Stepwise Multiple Regressions"
author: "Leah Thornton Hampton"
date: "2/1/2021"
output:
  html_document: 
    toc: true
    toc_depth: 4
    number_sections: true
    toc_float: true
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
#Packages
library(tidyverse)
library(MASS, exclude = 'select') #Stepwise regression package 
library(ggiraphExtra) #For plotting

@@

ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)
```

@@

```{r}
#Plots
ggPredict(m1_crust_model_dose,
          colorn=200,
 #         jitter=TRUE, 
point = FALSE,
          interactive = FALSE, 
show.summary = TRUE,
#digits = 3, 
se = FALSE)
```

@@

summary(m1_crust_model_particles)
```
plot
```{r}
ggPredict(m1_crust_model_particles, colorn=1000)
```
### volume
```{r}
#particle couunt
#Select the columns that we want to feed into the model for simplicity
m1_crust_volume <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.um3.mL.master = log10(dose.um3.mL.master)) %>% 
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.um3.mL.master, size.length.um.used.for.conversions)) %>% 
  drop_na()

@@

summary(m1_crust_model_volume)
```
plot
```{r}
ggPredict(m1_crust_model_volume, colorn=500)
```

@@

```{r}
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)
```

@@

ggPredict(m1_crust_model_dose,colorn=100,jitter=TRUE, interactive = FALSE, digits = 3, se = FALSE)

@@

```{r}
#Plots
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE)
```

```{r}
#alternative method using ggpredict
require(ggeffects)
require(ggdark)
require(ggsci)
ggpredict(m1_crust_model_dose)
df <- ggpredict(m1_crust_model_dose, se = TRUE)
df <- ggpredict(m1_crust_model_dose,terms=c("logdose.mg.L.master", "size.length.um.used.for.conversions"))

@@

```{r}
#alt method
plot(df, facet = TRUE)
```

@@

summary(m1_crust_model_discrete)
```
Plot.
```{r}
discrete <- ggpredict(m1_crust_model_discrete,terms = c("logdose.mg.L.master", "size_f"))
plot(discrete, facet = TRUE, add.data = TRUE)
```
### Survival package
```{r}
#include time
m1_crust <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.mg.L.master = log10(dose.mg.L.master)) %>% 
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.mg.L.master, size_f, exposure.duration.d)) %>% 
  drop_na()

require(survival)
survival <- survival::coxph(survival::Surv(exposure.duration.d, effect_10) ~ logdose.mg.L.master + size_f, data = m1_crust)
#cumulative hazard
cumHaz <- ggpredict(survival,terms = c("logdose.mg.L.master", "size_f"), type = "cumhaz")
plot(cumHaz, facet = TRUE, add.data = TRUE, colors = "flat")
```
```{r}
#survival probability over time
pr <- ggpredict(survival, c("logdose.mg.L.master", "size_f"), type = "surv")
plot(pr, colors = "social")
```

>>>>

---
title: "Stepwise Multiple Regressions"
author: "Leah Thornton Hampton"
date: "2/1/2021"
output:
  html_document: 
    code_folding: hide
    theme: sandstone
    toc: yes
    toc_float: yes
    toc_depth: 4
    number_sections: true
  word_document:
    toc: yes
---
```{r global-options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='Figs/',
                      warning=FALSE, message=FALSE, echo = FALSE)
```
---

```{r, echo = FALSE, message = FALSE, warning = FALSE}
#Packages
library(tidyverse)
library(MASS, exclude = 'select') #Stepwise regression package 
library(ggiraphExtra) #For plotting
library(ggeffects)
library(ggdark)
library(ggsci)
library(viridis)

@@

ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE, interactive = TRUE)
```

@@

```{r}
#Plots
ggPredict(m1_crust_model_dose,
          colorn=200,
 #         jitter=TRUE, 
point = FALSE,
          interactive = TRUE, 
show.summary = TRUE,
#digits = 3, 
se = FALSE)
```

@@

summary(m1_crust_model_particles)
```
plot
```{r}
ggPredict(m1_crust_model_particles, colorn=1000, interactive = TRUE)
```
### volume
```{r}
#particle couunt
#Select the columns that we want to feed into the model for simplicity
m1_crust_volume <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.um3.mL.master = log10(dose.um3.mL.master)) %>% 
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.um3.mL.master, size.length.um.used.for.conversions)) %>% 
  drop_na()

@@

summary(m1_crust_model_volume)
```
plot
```{r}
ggPredict(m1_crust_model_volume, colorn=500, interactive = TRUE)
```

@@

```{r}
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE, interactive = TRUE)
```

@@

ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE, interactive = TRUE)

@@

```{r}
require(ggiraphExtra)
#Plots
ggPredict(m1_crust_model_dose,colorn=100,jitter=FALSE, interactive = TRUE)
```

```{r eval=FALSE, include=FALSE}
#alternative method using ggpredict
require(ggeffects)
require(ggdark)
require(ggsci)
ggpredict(m1_crust_model_dose)
df <- ggpredict(m1_crust_model_dose, se = TRUE)
df <- ggpredict(m1_crust_model_dose,terms=c("logdose.mg.L.master", "size.length.um.used.for.conversions"))

@@

```{r eval=FALSE, include=FALSE}
#alt method
plot(df, facet = TRUE)
```

@@

summary(m1_crust_model_discrete)
```
Plotted below.
```{r}
discrete <- ggpredict(m1_crust_model_discrete,terms = c("logdose.mg.L.master", "size_f"))
plot(discrete, facet = TRUE, add.data = TRUE, colors = "quadro", alpha = 0.2, dodge = 0.2)
     #title = "All Aquatic Organisms")
```
#### Acute only crustacea
```{r, echo = FALSE}
require(arm) #bayesglm()
#Select the columns that we want to feed into the model for simplicity
m1_crust_acute <- aoc_setup %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(bio.org == "organism") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  filter(!effect_f == "NA") %>% 
  mutate(logdose.particles.mL.master = log10(dose.particles.mL.master)) %>% 
  mutate(logdose.mg.L.master = log10(dose.mg.L.master)) %>% 
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, 
                  logdose.mg.L.master, 
                  logdose.particles.mL.master, 
                  size_f)) %>% 
  drop_na()

#Fit the full model
m1_crust_acute_model_discrete <- glm(effect_10 ~ 
                                      logdose.mg.L.master * size_f  + 
                                       logdose.particles.mL.master * size_f, 
                                     data = m1_crust_acute, 
                                     na.action = "na.exclude", 
                                     family = "binomial"#,
                                     #glm.control(maxit = 50)
                                     )

summary(m1_crust_acute_model_discrete)
```
The above glm is visualized below.
```{r}
acute_discrete <- ggpredict(m1_crust_acute_model_discrete,terms = c(#"logdose.mg.L.master", 
                                                                    "logdose.particles.mL.master",
                                                                    "size_f")) #ensure discrete factor is second
plot(acute_discrete)#, facet = TRUE, add.data = TRUE)
```

#### Alt Method using GG Plot
This approach achieves a similiar product as using the ggPredict() function, except it relies on ggplot(), which is more malleable and transparent. The general steps are to first create a new dataframe over 1000 values of size using expand.grid() then use predict() and plot() with geom_line() and colour=size.
```{r}
require(viridis)
#filtered dataset
#m1_crust
#model
#summary(m1_crust_model_dose )
#generate distribution of data
mockData <- expand.grid(size.length.um.used.for.conversions = seq(0.034, 5000, 1),
            logdose.particles.mL.master = seq(-4.195, 12.650,0.1))

mockData$effect_10 <- predict(m1_crust_model_dose,
                     mockData,
                     type = "response")
#plot
mockData %>% 
  ggplot(aes(x = logdose.particles.mL.master, 
             y = effect_10, 
             color = size.length.um.used.for.conversions)) +
  geom_line() +
  scale_color_gradientn(colors = topo.colors(7)) +
  #scale_color_viridis_c(option = "A") +
  dark_theme_bw()
```

## Survival package
### Cumulative Hazard by Time
```{r}
#include time
m1_crust <- aoc_setup %>% 
  filter(!effect_f == "NA") %>% 
  #filter(effect.metric == c("HONEC", "LOEC", "NOEC")) %>% 
  #filter(organism.group == "Crustacea") %>% 
  filter(!acute.chronic_f == "Unavailable") %>% 
  filter(bio.org == "organism") %>% 
  filter(!environment == "Terrestrial") %>% 
  filter(lvl1_f == "Fitness") %>% 
  filter(!size_f == "Not Reported") %>% 
  mutate(logdose.mg.L.master = log10(dose.mg.L.master)) %>% 
 # filter(acute.chronic_f == "Acute") %>% 
  dplyr::select(c(effect_10, logdose.mg.L.master, size_f, exposure.duration.d)) %>% 
  drop_na()

require(survival)
survival <- survival::coxph(survival::Surv(exposure.duration.d, effect_10) ~ logdose.mg.L.master + size_f, data = m1_crust)
#cumulative hazard
cumHaz <- ggpredict(survival,terms = c("logdose.mg.L.master", "size_f"), type = "cumhaz")
plot(cumHaz, facet = TRUE, add.data = TRUE, colors = "flat")
```
### Probability of Survival by Time

```{r}
#survival probability over time
pr <- ggpredict(survival, c("logdose.mg.L.master", "size_f"), type = "surv")
plot(pr, colors = "social")
```
